\documentclass[11pt,a4paper,sans]{moderncv}

% Style and Color
\moderncvstyle{banking}  % Options: casual, classic, banking, fancy
\moderncvcolor{blue}      % Options: blue, orange, green, red, purple, grey

% Page Layout
\usepackage[scale=0.9]{geometry}  % Adjusts the page layout
\usepackage{lmodern}  % Ensures better font rendering
\usepackage{xcolor}  % Better color handling
\usepackage{hyperref}  % Clickable links
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

% Personal Information
\name{Ashraful}{Islam}
\title{Aspiring Machine Learning Engineer}
\address{Raozan, Chittagong, Bangladesh}{}
\phone[mobile]{+880 1935 188137}    
\email{ashrafdcc1502@gmail.com}  
\social[linkedin]{linkedin.com/in/ashraful-islam}
\social[github]{github.com/ashraf1600}

\begin{document}

% Displays Header
\makecvtitle  

% Career Objective
\section{Objective}
Passionate learner of \textbf{Machine Learning} and \textbf{Artificial Intelligence} with a background in \textbf{Software Engineering, Deep Learning, and AI-driven technologies}. Proficient in \textbf{Data Structures, Algorithms, and research methodologies}, with hands-on experience in \textbf{Machine Learning (ML) and Deep Learning (DL)}. Continuously improving skills in model building, data analysis, and algorithm optimization.

% Education
\section{Education}
\cventry{B.Sc. in Computer Science \& Engineering}{Chittagong University of Engineering and Technology (CUET)}{Jan 2023 – Ongoing}{}{}

\textbf{Academic Results:} Total 81.75 credits completed (Upto L-2,T-2)

\cvitem{L-1-T-1}{ CGPA 3.26 / 4.00}
\cvitem{L-1-T-2}{CGPA 3.10 / 4.00}
\cvitem{L-2-T-1}{CGPA 3.42/ 4.00}
\cvitem{L-2-T-2}{CGPA 3.72 / 4.00}

% Technical Skills
\section{Technical Skills}
\cvitem{Languages}{C, C++, Python, JavaScript, C\#}
\cvitem{Frontend}{HTML, CSS, Bootstrap, Tailwind CSS, React.js}
\cvitem{Backend}{Django, MySQL}
\cvitem{Machine Learning}{NumPy, Pandas, Matplotlib, Scikit-learn, TensorFlow, PyTorch}
\cvitem{Tools}{VS Code, GitHub, PyCharm, Google Colab}

% Competitive Programming
\section{Competitive Programming}
\cvitem{Experience}{Solved 500+ problems on Codeforces, LeetCode, and HackerRank. Participated in multiple programming contests. Context rating is 1150 }
\cvitem{Profiles}{\href{https://codeforces.com/profile/The_phoenix}{Codeforces}, \href{https://leetcode.com/u/noobashraf21/}{LeetCode}, \href{https://www.hackerrank.com/profile/ashrafdcc1502}{HackerRank}}

% Projects
\section{Projects}
\cvitem{\textbf{Calculator App}}{Developed a simple calculator using JavaScript.}
\cvitem{\textbf{Juice Shop}}{Built using APIs and JavaScript.}

% Activities
\section{Activities}
\cvitem{Organizing Secretary}{Cox’s Bazar Student Forum CUET (CSF) - Tree plantation event planning and engagement.}

% Interests
\section{Interests}
\cvitem{}{Machine Learning, AI Research, Software Engineering, Competitive Programming, Teaching, Learning new technologies.}

\end{document}
